Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
car ml cap
intro p

# Discussion
<!--
1. intro

TODO: somewhere ref:ml

7. from conclusions

box1: fitness
box2: extending qs
-->

<!-- intro -->
<!-- QW: could focus on just talking about the importance of scale for behavioural and spatial ecology. Why is it important and what are the more broadly applicable ideas that lead us to this paper -->

Complex animal social systems are influenced by biological and observation scales.
By parsing social systems into contexts using multilayer networks,
we observed differences across social, spatial and temporal scales.
Social scale
Spatial and temporal contexts 
including habitats, discrete patches and fragmented landscapes, as well as across 
seasonal differences in resource availability, or periods of migration, aggregation and disaggregation [@Kivela_2014; @Porter_2018; @Pilosof_2017]. 
Sociality exists across scales characterized by different 
types of behaviours as well as spatial and temporal thresholds defining these. 
Our results highlight the influence of social, spatial and temporal scales
on multilayer animal social networks, showing a requirement to consider biologically
relevant scales when selecting observational scales for a given study. 
<!-- intro -->

@@

(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest and open). Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

>>>>

# Discussion
<!--
1. intro
TODO: somewhere ref:ml
-->

<!-- intro -->
<!-- QW: could focus on just talking about the importance of scale for behavioural and spatial ecology. Why is it important and what are the more broadly applicable ideas that lead us to this paper -->
Animal social systems are characterized and influenced by three types of scale. 
Social scale defines the type and measurement of social relationships and directly
impacts observed sociality between individuals. Spatial scale, in this study,
reflects the resolution of the habitat within which social interactions occur. 
Finally, temporal scale is related to both study design and network robustness
as well as seasonal differences in resources, patch dynamics or
landscape connectivity. By parsing social systems into discrete contexts 
using multilayer networks, we highlight the influence of social, spatial and temporal scales
on animal social systems, demonstrating the importance of considering biologically
relevant and robust observational scales. 
<!-- intro -->

@@

(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest and open) informed by previous social, spatial and temporal scale analyses. Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
